Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
Henry study design

Diego is a 6 years hold child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplifiyed by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

@@

\subsubsection{Context, Study Design}
Henry is a five and half years hold child. It is followed by an occupational
therapist. According to the therapist, he presents visuo-constructive deficits.
From our perspective, the main effect of this trouble during handwriting
activity was that Henry
did not have any mental template to draw the shape of a letter. So he was 
apparently performing random attempts and then was comparing with the provided template.
What is more, Henry is strongly careless : he rarely payed attention to
advices, even to what he was doing when he was currently drawing, and he was
quickly shifting his attention from one
activity to another.
Hence, the goal of this study is to face those two chalenging issues
(visuo-constructive deficits and inattention) in order to keep Henry focused
on the activity during forty-minutes interactions, and to make the robot
evidently learning from his demonstrations.\\

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{abc-writer}
    \caption{\small Screenshot of the Android application developed to be used as
    pre-test and post-test: the child must follow with his finger the path of
the letter or number. We count the number of times the finger goes outside of
the red-bordered area.}
    \label{}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_demos}
    \caption{\small Henry's demonstrations for the number ``6'' (top row) and
        corresponding shapes generated by the robot. After eight demomstrations,
        Henry decided that the robot's ``6'' was good enough, and went to
    another character: in that respect, he was the one leading the learning
process of the robot.}
    \label{henry_demos}
\end{figure}

>>>>

Diego is a six years old child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplifiyed by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

@@

\subsubsection{Context, Study Design}
Henry is a five and half years old child. It is followed by an occupational
therapist. According to the therapist, he presents visuo-constructive deficits.
From our perspective, the main effect of this trouble during handwriting
activity was that Henry
did not have any mental template to draw the shape of a letter. So he was 
apparently performing random attempts and then was comparing with the provided template.
What is more, Henry is strongly careless : he rarely payed attention to
advices, even to what he was doing when he was currently drawing, and he was
quickly shifting his attention from one
activity to another.
Hence, the goal of this study is to face those two chalenging issues
(visuo-constructive deficits and inattention) in order to keep Henry focused
on the activity during forty-minutes interactions, and to make the robot
evidently learning from his demonstrations.\\

@@

Before the experiment, Henry was working on writing numbers with the therapist.
Hence we decided to turn the CoWriter activity to teach numbers to the robot. Build on
existing iPad application actually used by occupational therapists (Dawson Toth's \emph{ABC's
Writer}), we designed an Android application for pre-test and post-test. It consisted in drawing
numbers following an helping pattern, that becomes more fine with levels in
order to increase difficulty~\ref{fig:abc-writer}.\\

Since Henry was frequently drawing horizontaly inverted numbers, or even
absolutly unrecognizable shapes, we programmed the robot to refuse shapes that
was too distant to a reference with a threshold we arbitrary fixed. In that way,
the child was forced to take care on what he was providing to the robot as
demonstration. Also, to make sure the robot was going to improve its handwriting
and to clearly show this improvement, we decided to make it completly starting
from scratch : for all numbers, the first try of the robot resulted in
a simple vertical stroke (see the first robot's try in~\ref{learning_6_demos}).

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{abc-writer}
    \caption{\small Screenshot of the Android application developed to be used as
    pre-test and post-test: the child must follow with his finger the path of
the letter or number. We count the number of times the finger goes outside of
the red-bordered area.}
    \label{fig:abc-writer}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_demos}
    \caption{\small Henry's demonstrations for the number ``6'' (top row) and
        corresponding shapes generated by the robot. After eight demomstrations,
        Henry decided that the robot's ``6'' was good enough, and went to
    another character: in that respect, he was the one leading the learning
process of the robot.}
    \label{learning_6_demos}
\end{figure}
